---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# markers

<!-- badges: start -->
[![R-CMD-check](https://github.com/heike/markers/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/heike/markers/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of markers is to ...

## Installation

You can install the development version of markers like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(markers)
## basic example code
```


1. Load toolmarks
```{r}
load("data/toolmarks.RData")
```

2. Align by set

```{r}
library(tidyverse)
reps <- toolmarks %>% group_by(tool, plate, side, angle, direction, size) %>%
  tidyr::nest()
reps <- reps %>% mutate(
  aligned_set = data %>% purrr::map(sig_align_set, value=signature, group = mark)
)
```

3. Visualize

```{r, warning=FALSE, fig.height=10}
reps <- reps %>% 
  unite("id", tool, plate, side, remove = FALSE) %>%
  mutate(
  plot = purrr::map2(aligned_set, id, .f = function(d, id) {
    gg <- d %>% ggplot(aes(x =x, y = aligned, colour = factor(mark))) + geom_line() +
      theme_bw() + 
      ggtitle(id[1]) +
      theme(legend.position="none")
    gg
  })
)

library(gridExtra)
do.call(marrangeGrob, list(reps$plot[1:8], nrow=4, ncol=2))


ml = do.call(marrangeGrob, list(reps$plot, nrow=4, ncol=2))
ggsave("figures/multipage.pdf", ml)       
```
Download [pdf](multipage.pdf) with multiple pages of figures.

From Maria (Aug 2022)

The steps so far are: 

1. Convert stl files to x3p files and save in an appropriate folder

```{r eval = FALSE}
stls <- dir(pattern="stl", path="data/stl_files", full.names = TRUE)


for (file in stls) {
  stl_tool <- rgl::readSTL(file, plot=FALSE)
  x3p <- stl_to_x3p(stl_tool)
  x3p %>% x3p_write(file = gsub(".stl", ".x3p", file)) # not that this will re-name EVERY x3p by stl, i.e. no need to deal with stl_files to x3p_files separately
}

```


- signature extraction – I'm just filtering the signal from a set value of x to another. I bet this makes it so we lose some of the signal, but it's simple.
adding metadata –– So far I haven't run this code, so the x3p files don't have the correct metadata. Nina made a spreadsheet with this information, so all it would take is to run it, but it's slow.



- aligning signatures –– I'm still doing this my initial way instead of using your "markers" way because I added a piece in which all marks are the same length, 900 points, with NA fillers on either side. I figured this would make modeling easier. One thing I haven't done is to align the signals based on two criteria: the subset by tool (marks at different angles) and then by angle. When I tried aligning the marks made at different angles the alignment didn't look good.
- binning –– So far I've done this by choosing an arbitrary number of bins (18, so that each bin has 50 points in it). It would be nice if I could just change that number easily, e.g. b=22, and then the code would just run. The way it's written now it's way too dependent on the 18 bins.
- modeling –– The main task here has been calculating means by tool, and then the variance across tools. I couldn't figure out how to do this in general so you'll see it's quite specific. 

One more point:
- concatenating sides –– I'd like to start doing the whole analysis by using the signals from sides A and B of each tool concatenated. I think that is a more honest description of what the data are. That would have to be done after aligning, I think. 

